\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{amsmath}

\geometry{
legalpaper, total={177.8mm, 290mm},left=6mm, right=6mm,
top=7mm, bottom=12mm,
}

\usepackage{letltxmacro}

\usepackage{setspace}

\begin{document}


\begin{center}
Mymensingh Girls' Cadet College \\
$2^{nd}$ Term Fornightly Examination - 2025 \\
Subject: Statistics-I \\
Class: XI \\
Marks: 20 \hfill Time: 40 Minutes
\end{center}



\hrule


\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read 
the stems carefully and answer the associated questions. Answer all the questions.]\\
\end{center}

%\begin{center}
% \textbf{Group  - A}

%\end{center}
  \begin{enumerate}

  \item
\textbf{A software developer tracked the response times (in milliseconds) 
of a web application under test during peak usage hours. An unexpected 
delay of 1.2 ms was added to each recorded response time due to server
lag. The recorded times are as follows:}

\begin{center}
45, 48, 52, 50, 47, 53, 60, 55, 58, 49
\end{center}

\begin{enumerate}
    \item What is ordinal data? \hfill 1
    \item Explain change of origin and scale with an example. \hfill 2
    \item  
    Calculate $\displaystyle \sum_{i=1}^{10} (X_i - k)^2$, where $k$ is the last digit of your cadet number. \hfill 3
    \item
    Find the sum of the original response times before the lag was added. \hfill 4
\end{enumerate}

\textbf{Short-Answer Questions}

\item \textbf{Distinguish between the qualitative and quantitative variable.} \hfill $6 \times 0.5 = 3$

Diameter of trees, Color, Weight, Gender, Jersey Number, Family Size
\item Give one example of each scale of measurement. \hfill 2
    \item
	$x_1=2, x_2=-3, x_3=7, x_4=12.$ 
	
	Find the values of the following: \hfill $2 \times 2 = 4$
	
	i) $\displaystyle (\sum_{i=1}^3 x_i)^2$
	ii) $\displaystyle \sum_{i=1}^4 x_i^2$ 

\item Find $\displaystyle \sum_{i=1}^5 c$, where $c$ is a constant. \hfill 1

\end{enumerate}
\begin{center}
--- AAM ---
\end{center}
  \vspace{1cm}
  


\end{document}