\documentclass{article}
\usepackage{geometry}
\usepackage{amsfonts}

\geometry{
legalpaper, total={177.8mm, 290mm},left=20mm,
top=27mm, bottom=27mm,
}

\begin{document}

\begin{table}[h]
\centering
\begin{tabular}{lllll}
\textbf{\large SYLHET CADET COLLEGE} &  &  &  &  \\ \cline{4-5} 
TEST EXAMINATION - 2024 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Set} & \multicolumn{1}{l|}{C} \\ \cline{4-5} 
CLASS: XII &  &  &  &  \\ \cline{3-5} 
STATISTICS (CREATIVE)& \multicolumn{1}{l|}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{1} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{0} \\ \cline{3-5} 
SECOND PAPER &  &  &  &  \\
TIME – 2 hours \& 35 minutes &  &  &  &  \\
FULL MARKS – 50 &  &  &  & 
\end{tabular}
\end{table}
%  \normalfont\normalsize
 % 11.45a.m.~--~1.45p.m.

\hrule

\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read the stems carefully and answer the associated questions. Answer any \textbf{FIVE} questions taking at least two from each group.]\\

\end{center}

  \begin{center}
  \textbf{Group--A}
  \end{center}
    \begin{enumerate}
    
     \item
	  \textbf{Events that do not depend on each other are called independent events, and events that cannot occurr simulataneously are called disjoint events.} 
  
  \begin{enumerate}
    \item
	Provide an example of disjoint events, using the set theory. \hfill 1
    \item
	Prove that $P(A\cap \bar B) = P(A) - P(A\cap B)$ \hfill 2
    \item  
	If there are k mutually and exhaustive events, prove $\displaystyle \sum_{i=1}^k P(A_i) = 1$ \hfill 3
    \item
	Prove that two events cannot be simulataneously independent and mutually exclusive. \hfill 4
  \end{enumerate}

   \item
	  \textbf{Ratul and Tomal both have an unbiased die. Both have randomly thrown their dice once. } 
  
  \begin{enumerate}
    \item
	What are equally likely events? \hfill 1
    \item
	If a die is thrown once, what is the probability of getting a prime number? \hfill 2
    \item  
	From the stem, what is the probability that the sum of numbers appearing \\ on the dice is greater than 6. \hfill 3
    \item
	Examine: the probabilities of getting the sum less than 6 and greater than 6 are equal. \hfill 4
  \end{enumerate}
  
   \item
	  \textbf{The probability mass function (pmf) of a football striker scoring no. of hattricks during the course of a league season is given below}
	  
	  \begin{center}
	  $\displaystyle P(x)  = \frac{|2-x|}{k}; x = 0, 1, 2, 3, 4, 5$
	  \end{center}
  
  \begin{enumerate}
    \item
    What is a random variable? \hfill 1
    \item
		Is probability a discrete variable? Explain in brief. \hfill 2
    \item  
	Find the value of k.  \hfill 3
    \item
	Find the probability that the no. of hattricks would be less than the expectation. \hfill 4
  \end{enumerate}
  
     \item
	  \textbf{The probability distributions of demand of mobile phones of two operating systems (OS) Android (X) and iPhone OS (iOS) (Y) are:} 
	  
	    \begin{table}[h]
	    	  \begin{center}
\begin{tabular}{c|c|c|c|c|c}
Demand & 100  & 200  & 300  & 400  & 500  \\ \hline
P(X)   & 0.1  & 0.4  & m    & 0.15 & 0.1  \\ \hline
P(Y)   & 0.09 & 0.45 & 0.32 & 0.11 & 0.03
\end{tabular}
	  \end{center}
\end{table}
  
  \begin{enumerate}
    \item
	What is Expectation? \hfill 1
    \item
	Can Expectation be negative? \hfill 2
    \item  
	Find m from the table. \hfill 3
    \item
	Which OS has higher demand? Analyze. \hfill 4
  \end{enumerate}
  
    \begin{center}
  \textbf{Group--B}
  \end{center}
  
   \item
	  \textbf{A farmer selected a paddy field for seed collection. He found out that 10 out of each 25 paddies are damaged. He collected a sample of 15 paddies.} 
  
  \begin{enumerate}
    \item
	What is a Bernoulli trial? \hfill 1
    \item
	IF a trail is repeated n times, how many outcomes are generated? Explain. \hfill 2
    \item  
	Find the probability that at least one paddy is damaged? \hfill 3
    \item
	Comment on the skewness of the data. \hfill 4 
	
		[Hint: For a binomial distribution, $\gamma_1 = \frac{q-p}{\sqrt{npq}}$]
  \end{enumerate}
  
  \newpage
  
   \item
	  \textbf{Between 1000hrs and 1700 hrs, the average number of phonce calls per minute received by a power distribution company is 2.5. } 
  
  \begin{enumerate}
    \item
	Give an example where Poisson distribution is applicable. \hfill 1
    \item
	Find the relationship between expectationa and standard deviation of Poisson distribution. \hfill 2
    \item  
	Find the probability that the number of calls is between 1 and 3 (inclusive). \hfill 3
    \item
	What is the probability that the number of calls received is greater than the average? \hfill 4
  \end{enumerate}
  
   \item
	  \textbf{The frequency distribution of defective items in packets of key rings is given below.} 
	  
	  \begin{table}[h]
	  \centering
\begin{tabular}{c|c|c|c|c|c|c}
Number of defective items & 0 & 1 & 2 & 3 & 4 & 5 \\ \hline
Number of packets & 76 & 74 & 29 & 17 & 3 & 1
\end{tabular}
\end{table}
  
  \begin{enumerate}
    \item
	What is another way to write $P(X \ge 1)$? \hfill 1
    \item
	Can the mean of Poisson distribution be negative? \hfill 2
    \item  
	From the given stem, find mean and variance. \hfill 3
    \item
	Find the expected frequencies and comment. \hfill 4
  \end{enumerate}
  
   \item
  \textbf{For projection of population in a future time period, demographers use simple, \\ geometric or exponential growth technique. Each method has its advantages and \\ disadvantages.}

  \begin{enumerate}
    \item
	What is geometric growth? \hfill 1
    \item
    	In geometric growth method, obtain the formula for time required for the population to get \\ doubled [denote rate as r]. \hfill 2
    \item
    	In exponential method, how much unit of time is required for the population to get tripled?  \hfill 3
     \item
     	For projecting (predicting future values), is geometric growth method better than the \\ exponential method? Justify.  \hfill 4
  \end{enumerate}

\end{enumerate}

 \vspace{2.5cm}

\begin{center}

\end{center}

\end{document}