\documentclass{article}
\usepackage{amsfonts}
\usepackage{lipsum}
\usepackage[hidelinks]{hyperref}
\usepackage{titletoc}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{graphicx}

\geometry{
legalpaper, total={177.8mm, 290mm},left=20mm,
top=27mm, bottom=27mm,
}

\begin{document}

\begin{table}[h]
\centering
\begin{tabular}{lllll}
\textbf{\large SYLHET CADET COLLEGE} &  &  &  &  \\ \cline{4-5} 
PRE-TEST EXAMINATION - 2023 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Set} & \multicolumn{1}{l|}{D} \\ \cline{4-5} 
CLASS: XII &  &  &  &  \\ \cline{3-5} 
STATISTICS (CREATIVE)& \multicolumn{1}{l|}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{1} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{0} \\ \cline{3-5} 
 SECOND PAPER &  &  &  &  \\
TIME – 2 hours \& 35 minutes &  &  &  &  \\
FULL MARKS – 50 &  &  &  & 
\end{tabular}
\end{table}
%  \normalfont\normalsize
 % 11.45a.m.~--~1.45p.m.

\hrule

\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read the stems carefully and answer the associated questions. Answer any \textbf{FIVE} questions taking at least two from each group.]\\

\end{center}

  \begin{center}
  \textbf{Group--A}
  \end{center}
  
  \begin{enumerate}
  
     \item
	  \textbf{It is observed that 50\% of mails are spam. A software filters spam mail before reaching the inbox. Its accuracy for detecting a spam mail is 99\% and chances of tagging a non-spam mail as spam mail is 5\%.} 
  
  \begin{enumerate}
    \item
	What is a disjoint event? \hfill 1
    \item
	For two independent events, what does the Bayes' theorem reduce to? \hfill 2
    \item  
	What is the probability that a mail is tagged as spam?  \hfill 3
    \item
	If a certain mail is tagged as spam, find the probability that it is not a spam mail. \hfill 4
  \end{enumerate}

 \item
	  \textbf{Two dice are thrown together. The dice are named A and B.} 
  
  \begin{enumerate}
    \item
	What is P(A=7)? \hfill 1
    \item
	Create the sample space. \hfill 2
    \item  
	What is the probability that the outcomes of A \& B are different? \hfill 3
    \item
	Determine the probability that the summation of outcome of two dice is a prime number. \hfill 4
  \end{enumerate}
  
   \item
	  \textbf{$P(A) = \frac{3}{10}, P(B) = \frac 25, P(B\cup A) = \frac12$} 
  
  \begin{enumerate}
    \item
	What is an independent event? \hfill 1
    \item
	What is the relationship between independency and mutual excluvity? \hfill 2
    \item  
	Find $P(A \vert B)$ and $P(B \vert A)$ \hfill 3
    \item
	Verify the equality mathematically \& empirically: $P(B) = P(A) \cdot P(B \vert A) + P(\bar A) \cdot P(B \vert \bar A)$ \hfill 4
  \end{enumerate}
  
  
   \item
	  \textbf{A magician draws two cards from a pack (i) with replacement and then (ii) without replacement. The cards were well-shuffled before drawing.} 
  
  \begin{enumerate}
    \item
	What is the probability of an impossible event? \hfill 1
    \item
	How to determine the probability of a joint event?  \hfill 2
    \item  
	As per (i), what is the probability that the cards have different color? \hfill 3
    \item
	As per (ii), what is the probability that the cardsare aces of same color?  \hfill 4
  \end{enumerate}
  
    \begin{center}
  \textbf{Group--B}
  \end{center}
  
      \item
  \textbf{The probability density function of a continuous random variable is}

$$
  f(x) =
\begin{cases}
kx(x-1),  & 1 \le x \le 4 \\
0, & otherwise
\end{cases}
$$

  \begin{enumerate}
    \item
	What is the range of probability? \hfill 1
    \item
    	Find the value of k \hfill 2
    \item
    	Justify the pdf property of the fucntion. \hfill 3
     \item
     	What is the probability that X is greater than 3?  \hfill 4
  \end{enumerate}

  
     \item
	  \textbf{The probability distribution of a random X is provided below:} 
	  
	  \begin{table}[h]
	  \centering
\begin{tabular}{c|ccccc}
X & -1 & 0 & 1 & 2 & 3 \\ \hline
P(x) & $\frac 3{20}$ & $\frac 15$ & $\frac 14$ & $\frac 14$ & $\frac 3{20}$
\end{tabular}
\end{table}
  
  \begin{enumerate}
    \item
	What is the expectation of a constant m? \hfill 1
    \item
	Find $E(X).$ \hfill 2
    \item  
	Find $E(Y)$, where $Y = \frac X2$  \hfill 3
    \item
	Find Variance of (2X+3). \hfill 4
  \end{enumerate}

  
 \item
	  \textbf{A deck of 52 card is well-shuffled and three cards are drawn from them at random. The number of kings obtained is denoted by x.} 
  
  \begin{enumerate}
    \item
	What are equaly likely events? \hfill 1
    \item
	Differentiate between with replacement and without replacement drawings. \hfill 2
    \item  
	Form the probability fucntion using the above information and then form the distribution.\hfill 3
    \item
	Examine the statement: $P(1 \le x \le 3) = F(3)-F(1)$ \hfill 4
  \end{enumerate}
  
     \item
  \textbf{The joint probability function of two random variables X and Y is given below:}
  
  \begin{center}
  $\displaystyle P(X,Y) = \frac {x+2y}{16}; x = 0, 1; y = 0 ,1,2,3$
  \end{center}
 
  \begin{enumerate}
    \item
	Write down the formula of conditional proibability. \hfill 1
    \item
    	What is the relationship between marginal and joint probability? \hfill 2
    \item
    	Find P(X). \hfill 3
     \item
     	Find $P(X\vert Y)$ and $P(X\vert 0)$. \hfill 4
  \end{enumerate}

 \vspace{2.5cm}
 
\begin{center}
\textbf{\textit{“It is a capital mistake to theorize before one has data.”} – Sir Arthur Conan Doyle}
\end{center}
  
\end{enumerate}
\end{document}