\documentclass{article}
\usepackage{geometry}
\usepackage{amsfonts}



\geometry{
legalpaper, total={177.8mm, 290mm},left=20mm,
top=10mm, bottom=10mm,
}

\begin{document}

\begin{center}
  \bfseries\large
  Sylhet Cadet College

\normalsize
  Progress Test Examination - 2023

  Class: HSC

  Subject: Statistics Second Paper (Creative)

  Time: 2 hour \& 35 minutes \qquad \qquad \qquad Subject Code: 130  \qquad  \qquad \qquad Full Marks: 50

%  \normalfont\normalsize
 % 11.45a.m.~--~1.45p.m.
\end{center}

\noindent
\begin{tabular}{p{\dimexpr\linewidth-2\tabcolsep}}
  Answer FIVE questions taking at least two (2) from each group. Figures in the right indicate full marks.\\
  \hline
\end{tabular}

\begin{center}
\textbf{Group A}
\end{center}
  \begin{enumerate}
  \item
	  \textbf{An unbiased coin is tossed 10 times.} 
  
  \begin{enumerate}
    \item
	If a coin is flung 3 times, how many outcomes are generated? \hfill 1
    \item
	If a coin is flung n times, show how many outcomes are generated. \hfill 2
    \item  
	What is the probability of getting a) at least 3 heads, b) at most 3 heads? \hfill 3
    \item
	Are these probabilities equal? a) Getting at least 2 heads \& b) Getting at least 2 tails. \\ Also justify logically. \hfill 4
  \end{enumerate}

 \item
	  \textbf{The probability distribution of a discrete random variable X is given below:} 

	  \begin{table}[h]
	  \begin{center}
\begin{tabular}{c|cccccc}
x    & -2   & -1 & 0   & 1 & 3 & 4   \\ \hline
P(x) & 0.1 & k & 2k & 3k & 4k & 0.2
\end{tabular} 
\end{center}	
\end{table}
  
  \begin{enumerate}
    \item
	What is $\Sigma P(x)$? \hfill 1
    \item
	Find the value of k. \hfill 2
    \item  
	Find $P(X \geq 0)$ and $P(X < 1)$. \hfill 3
    \item
	Find the cumulative distribution function, F(X) and F(2) and explain. \hfill 4
  \end{enumerate}

   \item
	  \textbf{The probability distributions of demand of mobile phones of two operating systems (OS) Android (X) and iPhone (Y) are:} 
	  
	    \begin{table}[h]
	    	  \begin{center}
\begin{tabular}{c|c|c|c|c|c}
Demand & 100  & 200  & 300  & 400  & 500  \\ \hline
P(X)   & 0.1  & 0.4  & m    & 0.15 & 0.1  \\ \hline
P(X)   & 0.09 & 0.45 & 0.32 & 0.11 & 0.03
\end{tabular}
	  \end{center}
\end{table}
  
  \begin{enumerate}
    \item
	What is Expectation? \hfill 1
    \item
	Can Expectation be negative? \hfill 2
    \item  
	Find m from the table. \hfill 3
    \item
	Which OS has higher demand? Analyze. \hfill 4
  \end{enumerate}

\item
	  \textbf{An umbrella seller earns a revenue of BDT. 5000 if it rains. If it does not rain, he loses BDT. 1000. The probability that it rains on a given day is 0.04.} 
  
  \begin{enumerate}
    \item
	Write down the formula of Expectation for a continuous random variable. \hfill 1
    \item
	Can the value of Expectation be zero? \hfill 2
    \item  
	What is the umbrella seller's expected revenue? \hfill 3
    \item
	What should be the minimum probability of raining for him to achieve revenue greater than zero? \hfill 4
  \end{enumerate}

\begin{center}
\textbf{Group B}
\end{center}

 \item
	  \textbf{The number of defective pen produced by a company follows a binomial distribution with expectation 1.5 and variance 1.125.}. 
  
  \begin{enumerate}
    \item
	What is the mean of binomial distribution \hfill 1
    \item
	Can variance be greater than mean in binomial distribution? \hfill 2
    \item  
	Determine the probability function of the number of defective items produced by the company. \hfill 3
    \item
	What is the probability that the number of defective items is no less than 3? \hfill 4
  \end{enumerate}

  \item
	  \textbf{The number of customers coming at a shop per minute follows a Poisson distribution,  whose mean is 3.} 
  
  \begin{enumerate}
    \item
	What is a Poisson variate? \hfill 1
    \item
	Can the mean of Poisson distribution be negative? \hfill 2
    \item  
	Find the probability that the number of customers coming is between 1 and 2. \hfill 3
    \item
	Are the probabilities of coming to 2 and 3 customers equal?  \hfill 4
  \end{enumerate}
  
 \item
	  \textbf{A can manufacturer observes that 0.1\% of the produced cans are faulty. The cans are packaged in carton boxes, with 500 cans in each box. A wholeseller purchases 100 boxes from the manufacturer. } 
  
  \begin{enumerate}
    \item
	What is shape of Poisson distribution? \hfill 1
    \item
	For a Poisson distribution, P(2) = P (3). What is P(2)? \hfill 2
    \item  
	Find the probability of exactly one defective can. \hfill 3
    \item
	Find the expected number of boxes with no defective cans. \hfill 4
  \end{enumerate}  
  
    
   \item
	  \textbf{A reseracher uses the following data to know about some demographic characterisics.} 
  
  \begin{enumerate}
    \item
	What is General Fertility Rate? \hfill 1
    \item
	What is the difference between GRR and NRR? \hfill 2
    \item  
	Compute the population density. \hfill 3
    \item
	Are TFR and GRR same for this data? \hfill 4
  \end{enumerate}
  
  
  
\end{enumerate}
\end{document}