\documentclass{article}
\usepackage{geometry}
\usepackage{amsfonts}
\usepackage{float}

\geometry{
legalpaper, total={177.8mm, 290mm},left=20mm,
top=7mm, bottom=27mm,
}

\begin{document}

\begin{table}[h]
\centering
\begin{tabular}{lllll}
\textbf{\large SYLHET CADET COLLEGE} &  &  &  &  \\ \cline{4-5} 
TEST EXAMINATION - 2025 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Set:} & \multicolumn{1}{l|}{A} \\ \cline{4-5} 
CLASS: XII &  &  &  &  \\ \cline{3-5} 
STATISTICS (CREATIVE)& \multicolumn{1}{l|}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{1} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{0} \\ \cline{3-5} 
 SECOND PAPER &  &  &  &  \\
TIME – 2 hrs \& 35 minutes &  &  &  &  \\
FULL MARKS – 50 &  &  &  & 
\end{tabular}
\end{table}
%  \normalfont\normalsize
 % 11.45a.m.~--~1.45p.m.

\hrule

\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read the stems carefully and answer the associated questions. Answer any \textbf{FIVE} questions taking at least two questions from each group]\\
\end{center}

\begin{center}
\textbf{Group  - A}
\end{center}

  \begin{enumerate}
  
\item  
  \textbf{In a survey of 150 people, it is found that 70 own a car, 90 own a house, and 50 own both.}  

  \begin{enumerate}  
    \item What is a simple event? \hfill 1
    \item
How many different ways can a team of 4 players be selected from a group of 12 players? \hfill 2
    \item  
    What is the probability that a randomly selected person has only one item? \hfill 3  
    \item  
    	If a person is selected randomly, and if they do not own a house, what is the probability that they own a car? \hfill 4  
  \end{enumerate}  
  
  \item  
  \textbf{Two dice are thrown together. The dice are named A and B.}  

  \begin{enumerate}  
    \item  
    	What is the sample space for the possible outcomes of the two dice? \hfill 2  
    \item  
    	What is the probability that the absolute difference between the two dice is exactly 1? \hfill 3  
    \item  
    	What is the probability that the sum of the dice is a prime number and the outcome of die A is greater than that of die B? \hfill 4  
  \end{enumerate}  
  
   \item
	  \textbf{A deck of 52 card is well-shuffled and three cards are drawn from them at random. The number of kings obtained is denoted by x.} 
  
  \begin{enumerate}
    \item
	What are equaly likely events? \hfill 1
    \item
	Differentiate between with replacement and without replacement drawings. \hfill 2
    \item  
	Form the probability fucntion using the above information and then form the distribution.\hfill 3
    \item
	Examine the statement: $P(1 \le x \le 3) = F(3)-F(1)$ \hfill 4
  \end{enumerate}
  
  \item \textbf{A random variable is distributed as below:}

\begin{center}
  \textbf{$P(X) = \frac{7-\vert 5-x\vert}{k}; x=1,2,3,4,5,6$}
\end{center}

\begin{enumerate}
  \item
  	Find the value of k. \hfill 2
  \item
  	Determine the value of the expectation. \hfill 3
  \item
  	Find $V(4X-3)$ \hfill 4
\end{enumerate}


\begin{center}
\textbf{Group  - B}
\end{center}

\item  
  \textbf{A smartphone company finds that 9\% of its phones have minor defects. Each shipment contains 35 phones. A retailer purchases 500 shipments.}  

  \begin{enumerate}  
    \item  
      What is the probability that a randomly selected shipment has at most 3 defective phones? \hfill 3  
    \item  
      In how many shipments can we expect to find between 4 and 7 defective phones (inclusive)? \hfill 5  
  \end{enumerate}  

\item  
  \textbf{An emergency room receives an average of 3.8 patient arrivals per hour during nighttime (2200 hrs to 0600 hrs).}  

  \begin{enumerate}  
    \item  
      Find the probability that the number of patient arrivals in an hour is between 2 and 4 (inclusive). \hfill 3  
    \item  
      What is the probability that the number of arrivals exceeds 2? \hfill 4  
  \end{enumerate}  

\item  
  \textbf{The number of machine failures in a factory follows a Poisson distribution with a standard deviation of 2.5.}  

  \begin{enumerate}  
    \item  
      Find $P(X \geq 4)$. \hfill 3  
    \item  
      If $P(a) = P(a+2)$, what is the value of $a$? Does it hold for Poisson distribution?  \hfill 4  
  \end{enumerate}  
  
    \item
\textbf{A study was conducted to analyze the relationship between women's age groups and live births. The following table presents the number of women surveyed in different age groups along with the corresponding number of live births.} 

\begin{table}[H]
\centering
\begin{tabular}{c|c|c}
Age Group & No. of Women & No. of Live Births \\ \hline
15-19 & 540 & 109 \\ \hline
20-24 & 760 & 198 \\ \hline
25-29 & 530 & 86 \\ \hline
30-34 & 495 & 90 \\ \hline
35-39 & 450 & 65 \\ \hline
40-44 & 505 & 76 \\ \hline
45-49 & 430 & 60 
\end{tabular}
\end{table}

\begin{enumerate}
      \item Why is ASFR calculated for specific age groups instead of the entire population? \hfill 1
        \item Distinguish between TFR and GFR. \hfill 2
    \item
    Calculate the Age Specific Birth Rates (ASFR) for each age group. \hfill 3

    \item
    Compute the General Fertility Rate (GFR) and compare its value and concept with ASFR. \hfill 4
\end{enumerate}

  
\end{enumerate}

 \vspace{2.5cm}

\begin{center}
 “Quote” \\ -- Author
\end{center}

\end{document}