\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{amsmath}


\geometry{
legalpaper, total={177.8mm, 290mm},left=7mm, right=10mm,
top=7mm, bottom=27mm,
}

\begin{document}

\begin{table}[]
\begin{tabular}{llllllcllrlll}
\textit{Polaris} &  &  &  &  &  & \textbf{SYLHET CADET COLLEGE}       &  &                       & \multicolumn{1}{l}{}                        &                        &                        &                        \\ \cline{10-13} 
                 &  &  &  &  &  & TEST EXAMINATION - 2025             &  & \multicolumn{1}{l|}{} & \multicolumn{1}{c|}{Ques Setter}            & \multicolumn{3}{l|}{}                                                    \\ \cline{10-13} 
                 &  &  &  &  &  & CLASS: XII                          &  & \multicolumn{1}{l|}{} & \multicolumn{1}{c|}{Moderator}              & \multicolumn{3}{l|}{}                                                    \\ \cline{10-13} 
                 &  &  &  &  &  & STATISTICS (CREATIVE)               &  & \multicolumn{1}{l|}{} & \multicolumn{1}{c|}{VP}                     & \multicolumn{3}{l|}{}                                                    \\ \cline{10-13} 
                 &  &  &  &  &  & SECOND PAPER                        &  &                       &                                             &                        &                        &                        \\ \cline{11-13} 
                 &  &  &  &  &  & [According to the Syllabus of 2025] &  &                       & \multicolumn{1}{r|}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{1} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{0} \\ \cline{11-13} 
                 &  &  &  &  &  & TIME – 2 hours \& 35 minutes        &  &                       &                                             &                        &                        &                        \\
                 &  &  &  &  &  & FULL MARKS – 50                     &  &                       & \textbf{}                                   &                        &                        &                       
\end{tabular}
\end{table}

\hrule

\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read the stems carefully and answer the associated questions. Answer any \textbf{FIVE} questions taking at least two questions from each group]\\
\end{center}

\begin{center}
\textbf{Group  - A}
\end{center}

  \begin{enumerate}
  
   \item
	  \textbf{An analyst threw a coin and a die simultaneously and thought the events of getting a head from the coin and an even number from the die are independent.} 
  
  \begin{enumerate}
    \item
	What is a disjoint event? \hfill 1
    \item
	How are disjoint and independent events related? \hfill 2
    \item  
	Find the probability that the analyst does not get a head but gets a number \\ less than 4. \hfill 3
    \item
	Analyze the thought of the analyst. \hfill 4
  \end{enumerate}
  
     \item
	  \textbf{At CityHub High School, each student studies at least one language— Spanish, French, or Latin—and no student studies all three languages. 100 students study Spanish, 80 study French, 40 study Latin, and 22 study exactly two languages.} 
  
  \begin{enumerate}
    \item What is a sample space? \hfill 1
    \item How many different teams of 4 players can be formed from a group of 12 \\ players, always including a certain person? \hfill 2
    \item  
	How many students are there at the High School? \hfill 3
    \item
	If a student is selected at random, what is the probability that the student \\ studies only one language? \hfill 4
  \end{enumerate}

   \item
	  \textbf{The probability function of a discrete random variable is given below:} 
  
   \begin{center}
  $P(x) = \frac{x - 3}{6}, \quad \text{for } x = 4, 5, 6$
	  \end{center}
  
  \begin{enumerate}
   
     \item What is the property of a probability distribution regarding the sum of \\ all probabilities? \hfill 1
     \item If $a<b, F(b) - F(a) =$ ? where $F$ is cumulative distribution function? \\ Derive mathematically. \hfill 2
    \item  
	Find $F(x)$ and hence find and explain $F(5)$. \hfill 3
    \item
	If the range of the function is modified to icnlude 7, how can adjust the function to keep it valid? \hfill 4
  \end{enumerate}
  
          \item \textbf{A random variable is distributed as below:}
        
        \begin{center}
  \textbf{\[
P(x) = \frac{3x + 4}{21}, \quad x = 0, 1, 2
\]
}
  \end{center}

  \begin{enumerate}
    \item Write down the formula of $E(X^2)$ \hfill 1
    \item If $Y = 5X - 2$, Express $E\left(\frac{Y}{3} + 4\right)$ in terms of $E(X)$. \hfill 2
    \item
    	Determine the value of the expectation. \hfill 3
     \item
     	Find $V(4X-2)$ \hfill 4
  \end{enumerate}
  
% Questions here

\newpage

\begin{center}
\textbf{Group  - B}
\end{center}
  
  \item  
  \textbf{A university finds that 8\% of its printed course materials contain typographical errors. Each department orders 50 materials per term. Across the university, 600 departments place orders.}  

  \begin{enumerate}  
    \item What is $q$ in a binomial distribution? \hfill 1
    \item What happens if $n=1$ in Binomial distribution? \hfill 2
    \item  
      What is the probability that a randomly selected department receives at  most 3 erroneous \\ materials? \hfill 3  
    \item  
      How many departments are expected to receive at least 5 erroneous materials? \hfill 5  
  \end{enumerate}

   \item
	  \textbf{For a Binomial distribution, arithmetic mean = 4 and the variance is 3.} 
  
  \begin{enumerate}
     \item What is denoted by $X$ in Binomial distribution? \hfill 1
     \item What is the relationship between the mean, variance, and skewness in a binomial distribution? \hfill 2
    \item  
	Find $P(X = 3)$ \hfill 3
    \item
	Find and interpret the skewness of the distribution. \hfill 4
  \end{enumerate}
  
  \item
  \textbf{A website receives user sign-ups following a Poisson distribution, with a mean of 4 per hour.}  
  
  \begin{enumerate}
  \item How is the probability mass function (PMF) of a Poisson distribution expressed? \hfill 1
   \item
	Can the mean of Poisson distribution be negative? \hfill 2
    \item  
      What is the probability that exactly 2 or 3 users sign up in an hour? \hfill 3  
    \item  
      If $P(a) = P(b)$, comment on the combination of the values of $a$ and $b$. \hfill 4  
  \end{enumerate}
  
  
   \item
	  \textbf{The cities A and B have the following demographic characteristics:} 
  
  \begin{table}[H]
\centering
\begin{tabular}{c|c|c|c}
City & Area (sq km) & Population & No. of Females \\ \hline
A & 10,000 & 3.2 million & 1.9 million \\
B & 15,000 & 2.15 million & 1.1 million
\end{tabular}
\end{table}

  
  \begin{enumerate}
    \item How is dependency ratio calculated? \hfill 1
      \item Does population density alone determine the suitability of living in a city? \hfill 2
    \item  
	Which city has greater Sex Ratio? \hfill 3
    \item
	Which country is more comfortable for living? Justify your opinion. \hfill 4
  \end{enumerate}
  
\end{enumerate}

 \vspace{2.5cm}

\iffalse
\begin{center}
 “Quote” \\ -- Author
\end{center}
\fi




\end{document}