\documentclass{article}
\usepackage{geometry}
\usepackage{amsfonts}

\geometry{
legalpaper, total={177.8mm, 290mm},left=20mm,
top=7mm, bottom=27mm,
}

\begin{document}

\begin{table}[h]
\centering
\begin{tabular}{lllll}
\textbf{\large SYLHET CADET COLLEGE} &  &  &  &  \\ \cline{4-5} 
FIRST TERM-END EXAMINATION - 2024 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Set} & \multicolumn{1}{l|}{A} \\ \cline{4-5} 
CLASS: XII &  &  &  &  \\ \cline{3-5} 
STATISTICS (CREATIVE)& \multicolumn{1}{l|}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{1} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{0} \\ \cline{3-5} 
 SECOND PAPER &  &  &  &  \\
TIME – 2 hours \& 35 minutes &  &  &  &  \\
FULL MARKS – 50 &  &  &  & 
\end{tabular}
\end{table}
%  \normalfont\normalsize
 % 11.45a.m.~--~1.45p.m.

\hrule

\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read the stems carefully and answer the associated questions. Answer any \textbf{FIVE} questions taking at least two questions from each group]\\

\textbf{Group  - A}



\end{center}
  \begin{enumerate}

  \item
	  \textbf{A jar contains 5 red marbles and 7 yellow marbles. 
	  Three marbles are drawn at random.} 
  
  \begin{enumerate}
  \item What is a simple event? \hfill 1
  \item In how many different ways can 5 books be arranged on a shelf? \hfill 2
    \item  
	What is the probability that all marbles are yellow? \hfill 3
    \item
	What is the probability that a marble has a different color? \hfill 4
  \end{enumerate}

\item \textbf{\( P(M \vert N) = \frac{2}{9}, P(M \cup N) = \frac{5}{7}, P(N) = \frac{4}{7} \)}

\begin{enumerate}
  \item What is a certain event? \hfill 1
  \item Briefly explain empirical probability with an example. \hfill 2
    \item Calculate \( P(M \cap \bar{N}) \). \hfill 3
    
    \item Examine whether   \hfill 4
    
    i. $P(M \vert N) = P(N \vert M)$ \\
    ii. $P(M \cap \bar N) = P(\bar M \cap N)$
    
    \end{enumerate}
    
      \item
  \textbf{The joint probability function of two random variables \( X \) and \( Y \) is described by:}
  
  \begin{center}
  \( \displaystyle P(X,Y) = \frac{2x + y + 1}{52}; \quad x = 1, 2; \quad y = 1, 2, 3, 4 \)
  \end{center}
 
  \begin{enumerate}
  \item Give an example of a continuous random variable \hfill 1
  \item What are the required properties of a probability distribution? \hfill 2
    \item
    	Find the marginal distribution \( P(X) \). \hfill 3
    \item
     	Compute \( P(Y \vert X) \) for \( X = 2 \). \hfill 4
  \end{enumerate}
  
    \item
	  \textbf{The probability distributions of daily sales of two popular coffee brands, Brand A (X) and Brand B (Y), are:} 
	  
	    \begin{table}[h]
	    	  \begin{center}
\begin{tabular}{c|c|c|c|c|c}
Sales (cups) & 50   & 100  & 150  & 200  & 250  \\ \hline
P(X)         & 0.05 & 0.3  & p    & 0.25 & 0.1  \\ \hline
P(Y)         & 0.1  & 0.35 & 0.3  & 0.2  & 0.05
\end{tabular}
	  \end{center}
\end{table}
  
  \begin{enumerate}
  \item How can you expand $E(x+y)$? \hfill 1
  
  \item Determine the formula of variance in terms of expectation. \hfill 2
       \item  
	Find \( p \) from the table. \hfill 3
    \item
	Which brand has a more consistent daily sales distribution? Justify your answer. \hfill 4
  \end{enumerate}
  
  \begin{center}
\textbf{Group  - B}
\end{center}
  
    \item
	  \textbf{A company produces smartphones, and it is known that 5\% of the 
	  smartphones have \\ a manufacturing defect on average. The company ships 15 
	  smartphones in each box, \\ and a retailer purchases 500 boxes.} 
  
  \begin{enumerate}
  
   \item How many parameters does the Binomial distribution have? \hfill 1
   
   \item Can $V(X)$ be equal to $E(X)$ in binomial distribution? Examine. \hfill 2
    \item  
	What is the probability that the number of defective smartphones in a box 
	is at least 1? \hfill 3
    \item
	How many boxes are expected to contain exactly 2 defective smartphones? \hfill 4
  \end{enumerate}
  
    \item  
\textbf{A random variable is distributed as follows:}  

\begin{table}[h]
\centering
\begin{tabular}{c|c|c|c|c|c|c}
Value & 0 & 1 & 2 & 3 & 4 & 5 \\ \hline
Frequency & 60 & 80 & 50 & 20 & 6 & 2
\end{tabular}
\end{table}

\begin{enumerate}
 \item What is the mean of a Poisson distribution with parameter \( \lambda \)? \hfill 1
 
 \item If a Poisson distribution is $P(x) = \frac{e^{-m}m^x}{x!}, P(x+1) = ?$ 
 Derive in terms of $P(x)$. \hfill 2
    \item  
    Find the mean and standard deviation of the given distribution. \hfill 3
    \item  
    Compare the observed and expected frequencies, assuming a Poisson. \hfill 4
\end{enumerate}
  
   \item
	  \textbf{The number of cars passing through a toll booth follows a 
	  Poisson distribution with a \\ mean of 5 cars per minute.} 
  
  \begin{enumerate}
    \item What is a Poisson process?  \hfill 1
    \item Prove $\displaystyle \sum_{i=1}^{\infty} P(x) = \sum_{i=1}^{\infty} \frac{e^{-m} m^x}{x!} = 1$ \hfill 2
    \item  
	Determine the probability that exactly 3 cars pass through the toll 
	booth in a minute. \hfill 3
    \item
	If $P(X = a) = P(X = b)$, find the value of $a$ and $b$. What pattern do 
	you observe? \hfill 4
  \end{enumerate}
  
    \item
  \textbf{Population of New York, Los Angeles, and Chicago by different age groups and areas are given below:} 
  
  \begin{table}[!h]
  \begin{center}
  \begin{tabular}{lllll}
  City         & \multicolumn{3}{c}{Age}         & Area (sq. km) \\
               & 0-14      & 15-64    & 65+      &               \\
  New York     & 1,200,000 & 5,000,000 & 700,000  & 789           \\
  Los Angeles  & 1,000,000 & 4,500,000 & 500,000  & 1,302         \\
  Chicago      & 900,000   & 3,800,000 & 600,000  & 606           \\
  \end{tabular}
  \end{center}
  \end{table}
  
  \begin{enumerate}
    \item What is the formula of crude birth rate? \hfill 1
 \item Two dependency ratios are $d_1=98\%$ and $d_2=104\%$. 
  In which case are there more dependent people \\
  per 1000 individuals? \hfill 
    \item  
    Find and compare the dependency ratios of New York and Chicago. \hfill 3
    \item
    Based on the data, which city is more comfortable for living? Justify your
    choice. \hfill 4
  \end{enumerate}
  
\end{enumerate}
\end{document}