---
title: "Normal Distribution"
author: Abdullah Al Mahmud
date: \today
output: 
  revealjs::revealjs_presentation:
    theme: sky
    reveal_plugins: ["chalkboard", "zoom", "menu"]
    self_contained: false
    lib_dir: libs
    css: css/styles.css
    includes:
      in_header: css/header.html
---

# Most Important

It's the 

- most important distribution
- most common distribution
- most widely-used distribution

## Shape

```{r normal-density, echo=FALSE, fig.width=7, fig.height=5, fig.cap=""}
set.seed(123)         # for reproducibility
n <- 1000             # number of samples
mu <- 75               # mean
sigma <- 10            # standard deviation

# simulate data
x <- rnorm(n, mean = mu, sd = sigma)

# plot histogram scaled to density
hist(x,
     breaks = 30,
     probability = TRUE,
     col = "lightblue",
     border = "white",
     main = "Histogram with Normal Density Curve",
     xlab = "Value",
     ylim = c(0, max(density(x)$y, dnorm(mu, mu, sigma)) * 1.1))

# add theoretical normal density
curve(dnorm(x, mean = mu, sd = sigma),
      from = min(x) - 1,
      to = max(x) + 1,
      col = "red",
      lwd = 2,
      add = TRUE)

# add kernel density of the sample
lines(density(x), col = "darkgreen", lwd = 2, lty = 2)

# legend
legend("topright",
       legend = c("Theoretical normal", "Sample density"),
       col = c("red", "darkgreen"),
       lwd = 2, lty = c(1, 2))
``` 

## PDF

The normal PDF is given by

$$
f(x) = \frac{1}{\sigma\sqrt{2\pi}} e^{-\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^2}; -\infty <x<\infty
$$

> - First discovered by Abraham De Moivre

## Binomial to Normal

> - Number of trial (n) is large ($n \rightarrow \infty$)
> - $P(S) \approx P(\bar S$), where $S =$ Success

## Empirical Rule

68‑95‑99.7 Rule

```{r empirical-rule-base, echo=FALSE, fig.width=6, fig.height=5, fig.cap=""}
# 1. Numeric verification
p1 <- pnorm(1) - pnorm(-1)
p2 <- pnorm(2) - pnorm(-2)
p3 <- pnorm(3) - pnorm(-3)


# 2. Visual plot
x <- seq(-4, 4, length = 400)
y <- dnorm(x)
plot(x, y, type="l", lwd=2, col="blue",
     ylab="Density", xlab="Z",
     main="Standard Normal with ±1,2,3σ Shading")

# Function to shade region between -n and +n
shade_region <- function(n, col) {
  ix <- x >= -n & x <= n
  polygon(c(-n, x[ix], n), c(0, y[ix], 0),
          col = col, border = NA)
}

# Shade ±1, ±2, ±3
shade_region(3, rgb(0,0,1,0.1))
shade_region(2, rgb(0,0,1,0.2))
shade_region(1, rgb(0,0,1,0.3))

# Add legend
legend("topright",
       legend = c("±1σ ~68%", "±2σ ~95%", "±3σ ~99.7%"),
       fill = c(rgb(0,0,1,0.3), rgb(0,0,1,0.2), rgb(0,0,1,0.1)),
       border = NA)
```

## Properties

> - Bell-shaped 
> - Symmetrical about mean
> - $\beta_1 = 0, \beta_2 = 3$
> - $\mu = Me = Mo$
> - Area under whole curve is 1
> - The curve on either side of mean extends up to infinity.

## More Properties

> - Empirical rule
> - Linear combination of Normal $\rightarrow$ normal
> -  $MD(\bar X) \frac 45\sigma$
> - $QD = \frac 23\sigma$
> - $M_X(t) = \mathbb{E}[e^{tX}] = \exp\left(\mu t + \frac{1}{2} \sigma^2 t^2\right) -\infty \le t \le \infty$


