\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{amsmath}

\geometry{
legalpaper, total={177.8mm, 290mm},left=5mm, right=5mm,
top=7mm, bottom=12mm,
}

\usepackage{letltxmacro}

\LetLtxMacro\Oldfootnote\footnote

\newcommand{\EnableFootNotes}{%
  \LetLtxMacro\footnote\Oldfootnote%
}

\newcommand{\DisableFootNotes}{%
  \renewcommand{\footnote}[2][]{\relax}
}

\DisableFootNotes

\begin{document}

\iffalse
\begin{table}[]
\begin{tabular}{llcllcll}
 &  & \textbf{MYMENSINGH GIRLS’  CADET COLLEGE} &  &                                            & \multicolumn{1}{l}{}            &                        &                        \\
 &  & WHAT EXAMINATION - 2025                   &  &                                            &                                 &                        &                        \\
 &  & CLASS: WHAT                               &  &                                            &                                 &                        &                        \\
 &  & STATISTICS (CREATIVE)                     &  &                                            &                                 &                        &                        \\
 &  & WHAT PAPER                                &  &                                            & \multicolumn{1}{r}{}            &                        &                        \\ \cline{7-8} 
 &  & [According to the Syllabus of 2025]       &  & \multicolumn{1}{r}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{\textbf{1}} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{0} \\ \cline{7-8} 
 &  & TIME – 2 hours \& 35 minutes              &  &                                            & \multicolumn{1}{r}{}            &                        &                        \\
 &  & FULL MARKS – 50                           &  &                                            & \multicolumn{1}{r}{\textbf{}}   &                        &                       
\end{tabular}
\end{table}
\fi

\begin{table}[]
\begin{tabular}{llllllllcllcl}
\textit{Canopus} &  &  &  &  &  &  &  & \textbf{MYMENSINGH GIRLS’ CADET COLLEGE} &                                             &                                 & \multicolumn{1}{l}{}            &                        \\
                 &  &  &  &  &  &  &  & PRETEST EXAMINATION - 2025          &                                             &                                 &                                 &                        \\
                 &  &  &  &  &  &  &  & CLASS: XII                               &                                             &                                 &                                 &                        \\
                 &  &  &  &  &  &  &  & STATISTICS (CREATIVE)                    &                                             &                                 &                                 &                        \\
                 &  &  &  &  &  &  &  & FIRST PAPER                             &                                             &                                 & \multicolumn{1}{r}{}            &                        \\ \cline{11-13} 
                 &  &  &  &  &  &  &  & [According to the Syllabus of 2026]      & \multicolumn{1}{r|}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{\textbf{1}} & \multicolumn{1}{l|}{\textbf{2}} & \multicolumn{1}{l|}{9} \\ \cline{11-13} 
                 &  &  &  &  &  &  &  & TIME – 2 hours \& 35 minutes             &                                             &                                 & \multicolumn{1}{r}{}            &                        \\
                 &  &  &  &  &  &  &  & FULL MARKS – 50                          &                                             &                                 & \multicolumn{1}{r}{\textbf{}}   &                       
\end{tabular}
\end{table}


\hrule

\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read the stems carefully and answer the associated questions. Answer any \textbf{FIVE} questions taking at least two questions from each group]\\
\end{center}

\begin{center}
\textbf{Group  - A}
\end{center}
 \begin{enumerate}

  \item  
  \textbf{A nutritionist is analyzing the daily protein intake (in grams) of five athletes.  
  The recorded values are:}  
  \begin{center}
  $x_1 = 55,\quad x_2 = 60,\quad x_3 = 48,\quad x_4 = 62,\quad x_5 = 50$
  \end{center}

  \begin{enumerate}
  
  \item What is bivariate data? \hfill 1
  
  \item 
If the ages of a group of people are 22, 25, 28, 30, and 35, 
find $\displaystyle \sum_{i=1}^5 (x_i^2 + 3x_i)$ \hfill 2
    \item  
    Compute the value of $\displaystyle \sum_{i=1}^5 (x_i - 52)^2$ from the stem. \hfill 3

    \item  
    Calculate $\displaystyle \sum_{i=1}^5 (x_i^2 - 4x_i + 10)$ using both direct evaluation and by separating the summation terms. \hfill 4
  \end{enumerate}
  
       \item
	  \textbf{A departmental store records their sales. An analysis of products with prices less than tk. 30 generates the following table.} 
	  
\begin{table}[H]
\centering
\begin{tabular}{c|c|c|c|c|c|c}
Price     & 0-5 & 5-10 & 10-15 & 15-20 & 20-25 & 25-30 \\ \hline
Frequency & 1   & 0    & 2     & 3     & 8     & 12   
\end{tabular}
\end{table}
  
  \begin{enumerate}
    \item
	What is relative frequency? \hfill 1
    \item
	If $Y = a + bX$, $\bar Y = ?$ \hfill 2
    \item  
	Find 67th Percentile and 3rd Quartile and explain. \hfill 3
    \item
	Is AM or Median more suitable for this data? Elucidate. \hfill 4
  \end{enumerate}
  
   \item
	  \textbf{Given below is a series of data.} 
	  
	  	    \begin{center}
	 $5, 7, 9, \cdots , 123$
	    \end{center}
  
  \begin{enumerate}
    \item
	What is the summation of natural numbers up to nth value? \hfill 1
    \item
	Find the arithmetic mean of natural numbers from 1 up to 20. \hfill 2
    \item  
	Find the arithmetic mean of the given series. \hfill 3
    \item
	Prove that arithmetic mean is greater than gemetric mean theoretically and empricially. \hfill 4
  \end{enumerate}

 \item
	  \textbf{Two companies A and B pay their workers on a weekly basis. The summary of wages paid by them is shown below:} 
	  
	  \begin{table}[h]
	  \centering
\begin{tabular}{c|ccc}
Factory & Mean Wage (BDT) & Standard Deviation & Number of workers \\ \hline
A       & 1560       & 90                 & 200               \\ 
B       & 1580       & 70                 & 160              
\end{tabular}
\end{table}
  
  \begin{enumerate}
    \item
	What is dispersion? \hfill 1
    \item
	Is variance always greater than stanard deviation? Justify. \hfill 2
    \item  
	Which company is more consistent with their wages? \hfill 3
    \item
	Compare the wages with variance alone. Does it produce the same conclusion. Justify the finding.  \hfill 4
  \end{enumerate}
  
  
  \begin{center}
\textbf{Group  - B}
\end{center}

    \item
	  \textbf{A researcher wants to compare average life time of people in Bangladesh and other countries. He collected life time of 10 people in Bangladesh.} 
	  
	  	\begin{center}
	  75, 62, 63, 72, 66, 76, 59, 77, 70, 79
	  	\end{center}
  
  \begin{enumerate}
    \item
	What is symmetry? \hfill 1
    \item
	Mathematically show the theoretical value of the first central moment. \hfill 2
    \item  
	Compute the 2nd, 3rd, and 4th central moments of the data. \hfill 3
    \item
	Estimate skewness and kurtosis and explain. \hfill 4
  \end{enumerate}

 \item
	  \textbf{The first four moments about 3 of a distribution are -1, 5, -10, and 120.} 
  
  \begin{enumerate}
    \item
	What are moments used for? \hfill 1
    \item
	Can the second central moment be greater than the third central moment? \hfill 2
    \item  
	Find the second and third moments about arithmetic mean of the distribution. \hfill 3
    \item
	Find skewness and kurtosis and comment on the values.  \hfill 4
\end{enumerate}
  
    \item
  \textbf{The following table shows the monthly sales (in thousand ₹) of 8 salespeople and their years of experience. It is hypothesized that sales performance depends on experience.}

\begin{table}[h!]
\centering
\begin{tabular}{c|c|c|c|c|c|c|c|c}
Experience (X, years) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \hline
Sales (Y, thousand ₹) & 25 & 32 & 38 & 45 & 50 & 58 & 63 & 70 \\
\end{tabular}
\end{table}

\begin{enumerate}
\item What is correlation? \hfill 1
\item Write two purposes of regression analysis. \hfill 2
    \item
    Estimate and interpret the regression coefficient of y on x. \hfill 3
    
    \item
    Estimate the regression coefficient of x on y. Is this model realistic? Explain. \hfill 4
\end{enumerate}

  \item
\textbf{The monthly sales (in thousands of units) of a product for the last 6 months are given below:}

\begin{table}[h]
\centering
\begin{tabular}{ccccccc}
Month     & January & February & March & April & May & June \\ \hline
Sales     & 80      & 95       & 110   & 105   & 120  & 115  \\
\end{tabular}
\end{table}

\begin{enumerate}
 \item What is irregular variation? \hfill 1
\item How is moving average method used?  \hfill 2
\item
Determine the trend using the three-month moving average method. \hfill 3
\item
Plot the trend and forecast the sales for July using two methods 
and compare. \hfill 4
\end{enumerate}


  
\end{enumerate}

 \vspace{2.5cm}

\begin{center}

  \vfill
  --AAM--
\end{center}


\newpage
\setcounter{page}{1}

\begin{table}[]
\begin{tabular}{llllllllcllcl}
\textit{Orion} &  &  &  &  &  &  &  & \textbf{MYMENSINGH GIRLS’ CADET COLLEGE} &                                             &                                 & \multicolumn{1}{l}{}            &                        \\
                 &  &  &  &  &  &  &  & PRETEST EXAMINATION - 2025          &                                             &                                 &                                 &                        \\
                 &  &  &  &  &  &  &  & CLASS: XII                               &                                             &                                 &                                 &                        \\
                 &  &  &  &  &  &  &  & STATISTICS (CREATIVE)                    &                                             &                                 &                                 &                        \\
                 &  &  &  &  &  &  &  & FIRST PAPER                             &                                             &                                 & \multicolumn{1}{r}{}            &                        \\ \cline{11-13} 
                 &  &  &  &  &  &  &  & [According to the Syllabus of 2026]      & \multicolumn{1}{r|}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{\textbf{1}} & \multicolumn{1}{l|}{\textbf{2}} & \multicolumn{1}{l|}{9} \\ \cline{11-13} 
                 &  &  &  &  &  &  &  & TIME – 2 hours \& 35 minutes             &                                             &                                 & \multicolumn{1}{r}{}            &                        \\
                 &  &  &  &  &  &  &  & FULL MARKS – 50                          &                                             &                                 & \multicolumn{1}{r}{\textbf{}}   &                       
\end{tabular}
\end{table}


\hrule

\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read the stems carefully and answer the associated questions. Answer any \textbf{FIVE} questions taking at least two questions from each group]\\
\end{center}

\begin{center}
\textbf{Group  - A}
\end{center}
 \begin{enumerate}
 \item
	  \textbf{Marks obtained by five students in statisics out of 15 were 4, 6, 10, 12, and 15. The examiner said, the square of the sum of the marks is greater than the sum of the squares of the marks.} 
  
  \begin{enumerate}
    \item
	What is finite population? \hfill 1
    \item
	Explain quantitative variable with an example. \hfill 2
    \item  
	In the light of the available data, find $\displaystyle \sum_{i=1}^5 (x_i-2x_i)^2$ \hfill 3
    \item
	Verify the comment of the examiner. \hfill 4
  \end{enumerate}
  
       \item
	  \textbf{A sports analyst collected ages of athelets having ages between 10 and 35. He then presented his findings as below:} 
	  
	  \begin{table}[h]
	    \centering
\begin{tabular}{c|c|c|c|c|c}
Age            & 10-15 & 15-20 & 20-25 & 25-30 & 30-35 \\ \hline
No. of Athlete & 2     & 8     & 10    & 5     & 3    
\end{tabular}
\end{table}
  
  \begin{enumerate}
    \item
	What is central tendency? \hfill 1
    \item
	When is geometric mean iappropriate to measure? \hfill 2
    \item  
	Compute median from the stem. \hfill 3
    \item
	Show that Arithmetic mean is greater than Harmonic mean. Which one of them is more suitable for this data? \hfill 4
  \end{enumerate}

   \item
	  \textbf{A fridge manufacturing company observe temperatures of newly developed 8 deep fridges. The observed temperatures (in degree celsius are:} 
	  
	    \begin{center}
-10, -8, -2, -4, -4, -1, -12, -3, -13
  \end{center}
  
  \begin{enumerate}
    \item
	What is a Decile? \hfill 1
    \item
	How many Deciles does a data set have? Why? \hfill 2
    \item  
	Compute the 8th Decile from the data and explain. \hfill 3
    \item
	What is the value below which 75\% observations lie? Find in two distinct ways. \hfill 4
  \end{enumerate}
  
  
        \item
  \textbf{  A company recorded the monthly sales (in lakhs of ₹) of two salespersons X and Y for the first half of the year:}


\begin{table}[h]
\centering
\begin{tabular}{c|cccccc}
Month & Jan & Feb & Mar & Apr & May & Jun \\ \hline
Salesperson X & 42 & 38 & 45 & 40 & 43 & 41 \\
Salesperson Y & 50 & 28 & 60 & 35 & 55 & 30
\end{tabular}
\end{table}

\begin{enumerate}
 \item Does Range consider all values? \hfill 1
    \item Is $\sum |x_i-\bar x|$ always greater than $\sum (x_i-\bar x)$? Prove mathematically. \hfill 2
    \item Calculate the \textbf{mean deviation about median} for salesperson X. \hfill 3
    
    \item Which salesperson has \textbf{more consistent sales}? Justify using an appropriate relative measure of dispersion. \hfill 4
\end{enumerate}  
  
\begin{center}
\textbf{Group  - B}
\end{center}
  
 \item
	  \textbf{Marks obtained by a student in 7 subjects are} 
	  \begin{center}
	  70, 66, 55, 45, 80, 30, 82
	\end{center}
  
  \begin{enumerate}
    \item
	What is negative skewness? \hfill 1
    \item
	Draw graphs of positive and negative skewness showing the locations of mean and median. \hfill 2
    \item  
	Determine the five number summary from the stem and explain. \hfill 3
    \item
	Are the data symmetric? If not, comment on the pattern of data. \hfill 4
\end{enumerate}

   \item
	  \textbf{The first four moments around 2 of a dataset were the following:}
	  
	  \begin{center}
	  \textbf{-1, 5, 20, 90}
	  \end{center}
  
  \begin{enumerate}
    \item
	What is raw moment? \hfill 1
    \item
	What is the standard deviation of the data in the stem? \hfill 2
    \item  
	Determine the third central moment. \hfill 3
    \item
	Comment on the kurtosis of the given data. \hfill 4
  \end{enumerate}

\item
  \textbf{The table below displays the weekly hours of practice and corresponding tournament scores of 9 competitive tennis players. It is theorized that tournament score depends on practice hours.}

\begin{table}[h!]
\centering
\begin{tabular}{c|c|c|c|c|c|c|c|c|c}
Practice Hours (X) & 5 & 7 & 9 & 10 & 12 & 14 & 16 & 18 & 20 \\ \hline
Tournament Score (Y) & 45 & 52 & 60 & 68 & 75 & 82 & 88 & 93 & 98 \\
\end{tabular}
\end{table}

\begin{enumerate}
\item What is the range of correlation coefficient ($r$)? \hfill 1
\item $Y= a +bX;$ What does each notation mean  in regression context? \hfill 2
    \item
    Estimate and interpret the regression coefficient of y on x. \hfill 3
    
    \item
    Estimate the regression coefficient of x on y. Is this model realistic? Explain. \hfill 4
\end{enumerate}
  
\item
\textbf{The monthly website traffic (in thousands of visits) for an online platform over the past 7 months is provided below:}

\begin{table}[h]
\centering
\begin{tabular}{cccccccc}
Month & Jan & Feb & Mar & Apr & May & Jun & Jul \\ \hline
Visits & 42 & 48 & 55 & 52 & 60 & 65 & 70 \\
\end{tabular}
\end{table}

\begin{enumerate}
    \item What is the mulplicative model? \hfill 1
    \item Mention the methods of measuring the trend. \hfill 2
\item
Determine the trend using the three-month moving average method. \hfill 3
\item
Plot the trend and forecast traffic for August using two methods 
and compare. \hfill 4
\end{enumerate}  
\end{enumerate}

 \vspace{2.5cm}

\begin{center}
  \vfill
  --AAM--
\end{center}

\end{document}