\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{amsmath}

\geometry{
legalpaper, total={177.8mm, 290mm},left=6mm, right=6mm,
top=7mm, bottom=12mm,
}

\usepackage{letltxmacro}

\usepackage{setspace}

\LetLtxMacro\Oldfootnote\footnote

\newcommand{\EnableFootNotes}{%
  \LetLtxMacro\footnote\Oldfootnote%
}

\newcommand{\DisableFootNotes}{%
  \renewcommand{\footnote}[2][]{\relax}
}

\DisableFootNotes

\begin{document}
\setstretch{0.85}

\begin{table}[]
\begin{tabular}{llllllcllrlll}
\textit{Polaris} &  &  &  &  &  & \textbf{MYMENSINGH GIRLS' CADET COLLEGE}       &  &                       & \multicolumn{1}{l}{}                        &                        &                        &                        \\
                 &  &  &  &  &  & YEAR FINAL EXAMINATION - 2025             &  &                       & \multicolumn{1}{c}{}                        & \multicolumn{3}{l}{}                                                     \\
                 &  &  &  &  &  & CLASS: XI                         &  &                       & \multicolumn{1}{c}{}                        & \multicolumn{3}{l}{}                                                     \\
                 &  &  &  &  &  & STATISTICS (CREATIVE)               &  &                       & \multicolumn{1}{c}{}                        & \multicolumn{3}{l}{}                                                     \\
                 &  &  &  &  &  & FIRST PAPER                          &  &                       &                                             &                        &                        &                        \\ \cline{10-13} 
                 &  &  &  &  &  & [According to the Syllabus of 2026] &  & \multicolumn{1}{l|}{} & \multicolumn{1}{r|}{\textbf{Subject Code:}} & \multicolumn{1}{l|}{1} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{9} \\ \cline{10-13} 
                 &  &  &  &  &  & TIME – 2 hours \& 35 minutes        &  &                       &                                             &                        &                        &                        \\
                 &  &  &  &  &  & FULL MARKS – 50                     &  &                       & \textbf{}                                   &                        &                        &                       
\end{tabular}
\end{table}

\hrule

\begin{center}
[\textbf{N.B.} – The figures of the right margin indicate full marks. Read the stems carefully and answer the associated questions. Answer any \textbf{FIVE} questions taking at least two questions from each group]\\
\end{center}

\begin{center}
\textbf{Group  - A}
\end{center}

  \begin{enumerate}
  
     \item
	  \textbf{A system analyst collected frequencies of a signal at different times. Then he realized due to some unknown noise, 0.5 units got added to all the values. The recorded values are given below:} 
	  
	  \begin{center}
	  10, 12, 15, 14, 12, 16, 20, 16, 18, 11
	  \end{center}
  
  \begin{enumerate}
    \item
	What is change of origin? \hfill 1
    \item
	Does change of origin have an effect on median? \hfill 2
    \item  
	Find $\displaystyle \sum_{i=1}^{10} (X_i-5)$. \hfill 3
    \item
	Determine the summation of the values discarding the noise. \hfill 4
  \end{enumerate}
  
           \item
	  \textbf{Some of the most-searched key words on the web by the employees of a social media research firm are:}
	  
	  \begin{center}
    Facebook, Google, YouTube, Facebook, Facebook, YouTube, Weather, \\
YouTube, Gmail, YouTube, Facebook, YouTube, Google, YouTube, \\
Gmail, Weather, Gmail, Gmail, YouTube, Facebook, YouTube, \\
Gmail, Facebook, YouTube, Facebook
    \end{center}
    
  
  \begin{enumerate}
    \item What is most popular key word in the stem? \hfill 1
    \item Differentiate between primary and secondary data. \hfill 2
    \item  
	Draw a Bar Chart from the above data and explain. \hfill 3
    \item
	Is a Pie Chart a better representation of this data? Justify. \hfill 4
  \end{enumerate}

   \item
  \textbf{Frequency distribution of marks in statistics of a college is given in the following table.}
 

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|}
\hline
Marks & \begin{tabular}[c]{@{}c@{}}Number of Students\\ Group - A\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of Students\\ Group - B\end{tabular} \\ \hline
25-30 & 11 & 10 \\ \hline
30-35 & 18 & 16 \\  \hline
35-40 & 21 & 22 \\ \hline
40-45 & 26 & 28 \\ \hline
45-50 & 14 & 9 \\ \hline
\end{tabular}
\end{table}

  \begin{enumerate}
	\item When is Median a better measure of central tendency than Arithmetic Mean?  \hfill 1 
	\item Derive the formula of the combined arithmetic mean. \hfill 2
    \item  
	Calculate the arithmetic mean of Group - A \hfill 3
    \item
	Compute the combined mean. Is it greather than the arithmetic mean of Group - B? Explain the possible reason(s). \hfill 4
\end{enumerate}

    \item
  \textbf{Temperatures of two cold regions for five days are as below:}

    \begin{center}

    City A: 2, 1, -1, 0, 3

    City B: 3, 0, -2, 2, 3
    
    \end{center}
  \begin{enumerate}
    \item
	What is standard deviation? \hfill 1
    \item
	Is standard deviation of a set of negative values negative? Justify mathematically. \hfill 2
    \item  
	Find Mean Deviation about mean of the values of city A.  \hfill 3
    \item
	Which city has more consistent weather? Verify statistically. \hfill 4
\end{enumerate}

% Questions here

\begin{center}
\textbf{Group  - B}
\end{center}
  
     \item
	  \textbf{The first four moments around 4 of productions of a company over four years are -1.5, 17, -30, and 108.} 
  
  \begin{enumerate}
  \item What is skewness? \hfill 1
    \item
	Can the second central moment be negative? \hfill 2
    \item  
	Determine the second and third central moments. \hfill 3
    \item
	What kind of kurtosis do the data have? \hfill 4
  \end{enumerate}
  
     \item
	  \textbf{There has been an increase in average lifetime of people of Bangladesh. To get more insight on this, a research was conducted, in which ages of retired government employees were recorded. A sample of 10 people is given below:}
	  
	  \begin{center}
	  75, 62, 63, 72, 66, 76, 59, 77, 70, 79
	  \end{center}
    \begin{enumerate}
    \item
	What is the 2nd central moment equal to? \hfill 1
    \item
	Show that the first central moment is zero. \hfill 2
    \item  
	Find the variance of the data. \hfill 3
    \item
	Are the data symmetric? Justify. \hfill 4
  \end{enumerate}
  

  
  \item
	  \textbf{The temperature (in $^o$ Celsius) and rainfall (mm) in the city of Mymensingh on the last 6 raining days are summarized as below (temperature is denoted by $X$ and rainfall by $Y$: } 
	  
	  \begin{center}
	  $\sum x = 29, \sum y = 38, \sum xy = 205, \sum x^2 = 167, \sum y^2 = 282$
  \end{center}
  \begin{enumerate}
    \item
	What is covariance? \hfill 1
    \item
	Differentiate between cvariance and correlation. \hfill 2
    \item  
	Analyze the linear association between temperature and rainfall. \hfill 3
    \item
	Find the degree of impact of temperature on rainfall. \hfill 4
  \end{enumerate}

  
  \item
\textbf{The classification of published statistics is essential for organizing data into meaningful categories. This helps in better understanding and utilization of the data for research and policy-making.}

\begin{enumerate}
 \item What does BBS stand for?  \hfill 1
    \item Differentiate between official and non-official statistics. \hfill 2
    \item  
    Explain the classification system used for published statistics in Bangladesh. \hfill 3
    \item
    Evaluate the effectiveness of this classification system in meeting the needs of researchers and policymakers. \hfill 4
\end{enumerate}

  
\end{enumerate}

 \vspace{2.5cm}

\begin{center}

  \vspace{2.5cm}
  
\vfill  --- Abdullah Al Mahmud ---
\end{center}

\end{document}